Online Balanced Graph Partitioning: Optimizations for Large Clusters

### 2020-05-03 paper/disc20clustering.tex
Comments
Related work update

\noindent \textbf{Contributions.}
We provide an improved lower bound 
of $\Omega(k\cdot\ell)$ on the competitive ratio of any online deterministic online algorithm 
even in the learning model;
the best known lower bound so far was $\Omega(k)$,
even for a more general model~\cite{repartition-disc}.
We also present an asymptotically optimal, 
$O(k\cdot \ell)$-competitive algorithm
for the learning model.
For the repartitioning model, we present  
an asymptotically optimal,
$\Theta(\ell)$ algorithm for $k=3$;
the best known upper bound 
so far was $O(\ell^2)$~\cite{repartition-disc}.
Then, we present a strictly $6$-competitive algorithm for $k=2$.
In addition, we show a new, improved analysis of the algorithm from \cite{repartition-disc} that depends on the solutions to an interesting combinatorial problem (see Section~\ref{ssec:cascade}, The Cascade Problem).
%
The overview of known results is in Table~\ref{tab:overview}.

@@

\noindent \textbf{Related work.}
The existing results in~\cite{repartition-disc}
and~\cite{sigmetrics19_partitioning}
primarily focus on a model where 
the online algorithm can use augmentation,
i.e., has slightly larger clusters than the offline 
algorithm. In contrast, in our paper, we focus
on a scenario where the nodes need to be
perfectly balanced among the clusters.
The problem has also been studied in a weaker
model where the adversary can only sample
requests from a fixed distribution~\cite{stochastic-ring}.
For clusters of size $2$ (i.e., $k=2$), 
it is known that a $7$-competitive algorithm exists~\cite{repartition-disc} with large ($\Omega(\ell^2)$) additive constant.

@@

>>>>

\noindent \textbf{Contributions.}
We provide an improved lower bound 
of $\Omega(k\cdot\ell)$ on the competitive ratio of any online deterministic online algorithm 
even in the learning model;
the best known lower bound so far was $\Omega(k)$,
even for a more general model~\cite{repartition-disc}.
We also present an asymptotically optimal, 
$O(k\cdot \ell)$-competitive algorithm
for the learning model.
For the repartitioning model, we present  
an asymptotically optimal,
$\Theta(\ell)$ algorithm for $k=3$;
the best known upper bound 
so far was $O(\ell^2)$~\cite{repartition-disc}.
Then, we present a strictly $6$-competitive algorithm for $k=2$ that improves upon previous $7$-competitive algorithm with $O(\ell^2)$ additive constant..
In addition, we show a new, improved analysis of the algorithm from \cite{repartition-disc} that depends on the solutions to an interesting combinatorial problem (see Section~\ref{ssec:cascade}, The Cascade Problem).
%
The overview of known results is in Table~\ref{tab:overview}.

@@

\section{Related work}

In the paper that originated a study on BRP \cite{repartition-disc} (DISC 2016), authors provided a $O(k^2 \cdot \ell^2)$-competitive algorithm, and a lower bound $\Omega(k)$.
For $k=2$, they presented a $7$-competitive algorithm~\cite{repartition-disc} with substantial ($\Omega(\ell^2)$) additive constant.

The existing results in~\cite{repartition-disc}
and~\cite{sigmetrics19_partitioning}
primarily focus on a model where 
the online algorithm can use augmentation,
i.e., has slightly larger clusters than the offline 
algorithm. In contrast, in our paper, we focus
on a scenario where the nodes need to be
perfectly balanced among the clusters.
The problem has also been studied in a weaker
model where the adversary can only sample
requests from a fixed distribution~\cite{stochastic-ring}.

@@

\maciek{The big inequality is impressive, but not a lot change in each row. Instead, bound the cost of ALG separately in one line, and the cost of OPT in another. (possibly far away from eachother)}
